Measuring variation in gaze following across communities, ages, and individuals --- a showcase of the TANGO--CC

### 2024-06-12 paper/manuscript.tex
incorporate co-author feedback

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\usepackage{libertine}
\captionsetup[figure]{font={stretch=1}}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology\\\textsuperscript{3} Budongo Conservation Field Station\\\textsuperscript{4} School of Psychology, University of Auckland\\\textsuperscript{5} Université Marien Ngouabi\\\textsuperscript{6} Department of Psychology, Stanford University\\\textsuperscript{7} School of Psychology, University of Plymouth\\\textsuperscript{8} Department of Psychology, Koç University\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia\\\textsuperscript{11} Department of Psychology, University of York\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for investigating the universality and robustness of cognitive developmental processes. Yet, suitable methods to measure variability in cognition across languages and communities are lacking. This paper describes the TANGO--CC (Task for Assessing Individual Differences in Gaze Understanding -- Cross-Cultural), a gaze following task designed to measure basic social cognition across individuals, ages, and communities. The TANGO--CC was developed and psychometrically assessed in one setting and subsequently adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO--CC captured individual differences and showed good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task. The TANGO--CC represents a valuable contribution to assessing basic social cognition in diverse communities, establishing a roadmap for researching cross-cultural individual differences.
}

@@

For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on participants from Western, Educated, Industrialized, Rich, and Democratic (WEIRD) communities (Henrich et al., 2010; Lillard, 1998).
Despite numerous calls for change, the subject pools reported in high-impact journals still lack diversity (Gutchess \& Rajaram, 2023; Nielsen et al., 2017).
This lack of representation hinders progress in theory building: inferences about the universal and variable aspects of the human cognitive system cannot be drawn from data collected in single communities (Krys et al., 2024).

One reason for the lack of diversity in psychological studies is the scarcity of suitable methods to collect comparable psychological data in different communities (Bourdage et al., 2023). This shortage of suitable measures is even more prevalent in developmental psychology. In this paper, we describe the construction and psychometric evaluation of a measure of basic social cognition (gaze following) in children as a concrete example for how to overcome this problem.

Studies investigating variation between communities and/or individuals need to ensure that the captured variation is systematic and not just random noise: measures need to be reliable and valid.
This, of course, applies to all fields of psychology. Given the topic of this paper, we will focus on measures of social cognition for children. Studies on social cognition based on US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020).
This picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
Thus, it is already challenging to find reliable and valid tasks that can capture individual differences within one community, let alone tasks that do so across different communities.

Adapting tasks to diverse communities and re-assessing their validity and reliability might be especially important in the social-cognitive domain.
If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, the tasks need to represent different communities.
Indeed, task performance can be diminished when stimuli are not adjusted (Peña, 2007).
For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.
This underlines the importance of adapting tasks to each specific cultural context.

Broadly speaking, there are two different approaches that researchers can take to collect cross-cultural data.
One approach would be to translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
While this approach is most flexible and sensitive to cultural differences, it might be most feasible for studying up to a handful of communities as it becomes too demanding and time-consuming.
Most importantly, this approach assumes that the measured underlying concept is the same, while absolute task scores are not comparable across the communities.
Another approach would be to use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of culturally inappropriate stimuli (termed ``adoption'' and ``adaptation'', respectively; He and Vijver (2012), Waschl and Chen (2022)).
This approach is less sensitive to each community's unique characteristics but allows for a direct comparison of the data across communities.
Examples following this approach include Callaghan et al. (2011), Taumoepeau et al. (2019), Hughes et al. (2018), Hughes et al. (2014), Fujita et al. (2022), Mehta et al. (2011), Stengelin et al. (2020), and Chasiotis et al. (2006).
The present paper aims to describe the development and psychometric properties of a standardized task that can be adapted to diverse communities.

The task presented here focuses on gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
While gaze following is one of the most fundamental social-cognitive abilities, studies focusing on cultural variations are rare.
The few existing results are mixed on whether gaze following is influenced by cultural factors or not (Callaghan et al., 2011; Hernik \& Broesch, 2019).

The task presented here builds upon the TANGO (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
The TANGO measures participants' imprecision in locating an agent's attentional focus.
It has been shown to reliably capture individual differences in a German child sample and an English-speaking remote adult sample.
The task was sensitive to developmental changes and linked to children's receptive vocabulary.
Furthermore, an exploratory analysis showed that children performed equally well in a task version with animal faces compared to cartoon human faces (Prein et al., 2024).
This suggests that superficial variations in the stimulus design do not influence children's performance in the task.

This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that can be -- and has been -- adapted to several languages and communities.
We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
We assess its cross-cultural applicability based on data from a large cross-cultural sample of 2.5- to 11-year-olds from 17 different urban/rural communities across the world and discuss the task's psychometrics.
The task and all its adaptations have been initially designed for a paper by Bohn et al. (2024), and we re-use the data set in this paper.

@@

In a perfect world, developing a cross-cultural task would include international collaboration and diverse samples from the beginning, already during study design, piloting and item selection.
As this seems hardly feasible, we present a pragmatic approach.
The TANGO-CC was first implemented in one context, in our case Leipzig, Germany (Prein et al., 2023).
Here, the task's reliability and validity were assessed in detail.
Even though this does not guarantee that the task will be valid and reliable in another context, it substantially increases the likelihood.
Second, we reassessed the TANGO--CC's measurement quality (i.e., variability and reliability) across diverse communities by analyzing the data from Bohn et al. (2024), who used the task to collect data in 17 communities.
Therefore, our procedure maintains a balance between a detailed analysis of the task's psychometric properties and a swift and feasible task adaptation.
In the following, we describe the different steps in further detail.
We hope that not just the TANGO--CC but also our pragmatic approach to constructing it will be helpful for other researchers.

In the first step, the task's underlying structure was designed.
The TANGO--CC measures the precision with which participants locate an agent's attentional focus.
The participant's task is to locate a target by following the agent's gaze (see Figure \ref{fig:fig1}).
Precision was measured in a continuous way as the distance between the participant's click on the screen (\emph{i.e.}, where the participant thinks the target is) and the target's real position.
The task's core functionality is to animate the agent's eyes so that they follow the target's movement.
This basic structure was then embedded in the task's superficial appearance (e.g., background scene) and audio instructions.
Once this structure was implemented, adaptations of the task were greatly simplified.
For example, we can change the background scene, the faces of the agent, and the target without changing how and what the task measures.

This basic version of the TANGO was psychometrically evaluated in a prototypical WEIRD sample (German child sample; English-speaking remote adult sample) and was found to be highly reliable and valid (Prein et al., 2023).
While participants got more and more precise in locating the attentional focus of the agent the older they were, individuals differed across all age groups and showed no floor- or ceiling effects.
Performance in the TANGO was linked to children's receptive vocabulary and weakly related to factors of children's daily social environment.
In another study, Prein et al. (2024) proposed a computational cognitive model that described gaze following as a social form of vector following.
Gaze following, as measured by the TANGO, was related to children's non-social vector following and visual perspective-taking abilities.
These connections to related constructs indicate the task's validity in the tested WEIRD setting.

To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces that were judged by researchers and research assistants from each target community to be representative of the local population (see Figure \ref{fig:fig1}).
Similarly, different backgrounds were created that roughly represented a typical accommodation in each community.
Audio instructions were translated into the corresponding local language.
By back-translating these instructions, we ensured the original meaning did not change.
Sometimes, specific words were linguistically slightly modified, although functionally equivalent (e.g., ``bush'' instead of ``hedge''), to ensure that all participants understood the instructions.
In the following, we describe how researchers can use and customize the TANGO--CC in more detail.

@@

We quickly recap the TANGO's (Prein et al., 2023) most characteristic features: Participants are asked to locate a balloon with the help of a gaze cue.
The task consists of three different trial types (see Figure \ref{fig:fig1}).
In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
The balloon falls down to the ground, while the eyes of the agent follow the movement of the balloon in a way that their centers always align.
Depending on the trial type, participants have different visual access to the balloon's position.
In training 1, participants see the full trajectory of the balloon and directly have to touch the balloon itself.
In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
The first trial of each type contains an audio description of the presented events (see supplements of Bohn et al. (2024)).
Notably, the instructions explicitly state that the agent is looking at the balloon.

The outcome variable is the distance between the participant's touch and the balloon's center.
Trials can be completed quickly and efficiently so that children can easily complete 15 trials within 10 minutes.
This drastically reduces drop-out rates.
By using essentially self-explanatory animations, language demands are kept to a minimum.
No differential feedback is given to keep trials comparable and avoid learning effects.

@@

The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
For the balloon positions, the entire width of the screen (1920 in ``SVG units'') is divided into ten bins.
Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
If the total number of trials is not divisible by the number of unique elements, additional elements are randomly selected to make up for the remainder.

@@

The TANGO--CC can be accessed via the following link: (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).
In the first step, researchers can select the language for audio instructions, currently available for 13 different languages and even more dialects (see Table 1).
All written instructions are presented in English because they are not directed to the participant but to the research assistant who guides the participant through the task.
The task can either be started with the default settings or further customized.
The default settings use the version applied in Bohn et al. (2024) based on the selected language.

If researchers choose to customize the task (see Figure \ref{fig:fig1}), the number of trials can be chosen for each trial type.
As the trial types build up on each other, each trial type is necessary to understand the structure of the task and needs to be completed before the next trial type starts.
Therefore, no trial type can be skipped.
The minimum number of trials per type is 1; the maximum is 100.
One out of four different backgrounds can be selected.
Finally, there are 50 diverse human faces (50\% female, 50\% male) from which researchers can choose.
No constraint exists on how many faces are allowed (min 1, max 50).
Once all the settings are adjusted, the customized task is compiled.

In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed.
To save the selected settings, researchers can bookmark the URL so that the customized task can be easily accessed, and only the participant ID and choice of webcam recording need to be entered again.
The task can then be started.

The source code of the task is available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers gain even more flexibility in adjusting the task to their needs.

@@

\caption{\label{tab:langtab}Languages available for the audio instructions in the TANGO--CC}

\begin{tabular}{lll}
\toprule
Languages & \multicolumn{1}{c}{Language family} & \multicolumn{1}{c}{Speaker's country of origin}\\
\midrule
Bemba & Bantu & Zambia\\
Chinese & Sino-Tibetan & China\\
English & Indo-European & USA / UK / India / Nigeria / New Zealand\\
German & Indo-European & Germany\\
Hai||om & Khoesan & Namibia\\
Khewdam & Khoesan & Namibia\\
Lingala & Bantu & Rep. Congo\\
Marathi & Indo-European & India\\
Shona & Bantu & Zimbabwe\\
Spanish & Indo-European & Argentina / Mexico\\
Swahili & Bantu & Uganda\\
Turkish & Turkic & Türkiye\\
Yaka & Bantu & Rep. Congo\\
\bottomrule
\end{tabular}

@@

{\centering \includegraphics[width=1\linewidth]{../figures/TANGO-CC-procedure}

@@

\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions, the number of trials per trial type, the background, and the agent's face. Screenshots of the trials show the proceeding events: In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by touching the balloon. In training 2, the balloon falls behind the hedge while its flight is still visible. Participants respond by touching the hedge where they think the balloon is. In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by touching the hedge. In the task, all movements are smoothly animated (no still pictures). Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
\end{figure}

@@

The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS} and is presented as a web app.
It can be accessed on any web browser and does not require prior installation.
The online version of the task has been proven convenient for unsupervised data collection (for example, using participant recruitment services like \emph{Prolific}; see Prein et al. (2023)) and sharing the task internationally.
Importantly, the web app implementation does not necessarily need a working WIFI connection: An offline, local version of the task can be quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
This is an especially useful feature for researchers working in remote areas with limited internet access.

The stimuli are embedded as Scalable Vector Graphics (SVG).
The setup allows for an easy adaptation of task elements and ensures that picture quality, aspect ratio, and relative object positioning are constant.
The task is programmed so that responses are only registered when the participant touches the relevant part of the screen (i.e., in test trials, the hedge).
Furthermore, clicks are only registered after the voice recordings stop playing.
An audio reminder is played again if no click is registered within 5 seconds.

>>>>

\linenumbers
\usepackage{csquotes}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{unicode-math}
\usepackage{setspace}
\usepackage{libertine}
\captionsetup[figure]{font={stretch=1}}
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\typesectitle}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Institute of Psychology in Education, Leuphana University Lüneburg, Germany\\\textsuperscript{2} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Germany\\\textsuperscript{3} Budongo Conservation Field Station, Uganda\\\textsuperscript{4} School of Psychology, University of Auckland, New Zealand\\\textsuperscript{5} Université Marien Ngouabi, Republic of the Congo\\\textsuperscript{6} Department of Psychology, Stanford University, USA\\\textsuperscript{7} School of Psychology, University of Plymouth, UK\\\textsuperscript{8} Department of Psychology, Koç University, Türkiye\\\textsuperscript{9} Division of Psychology, Communication, and Human Neuroscience, University of Manchester, UK\\\textsuperscript{10} Department of Psychology and Social Work, University of Namibia, Namibia\\\textsuperscript{11} Department of Psychology, University of York, UK\\\textsuperscript{12} CAS Key Laboratory of Behavioral Science, Institute of Psychology, Chinese Academy of Sciences, China\\\textsuperscript{13} Department of Psychology, Developmental Psychology, Uppsala University, Sweden\\\textsuperscript{+} joint last author}

\abstract{%
Cross-cultural studies are crucial for investigating cultural variability and universality of cognitive developmental processes. However, cross-cultural assessment tools in cognition across languages and communities are limited. This paper describes a gaze following task designed to measure basic social cognition across individuals, ages, and communities (Task for Assessing iNdividual Differences in Gaze understanding Open -- Cross-Cultural or TANGO--CC). The TANGO--CC was developed and psychometrically assessed in one cultural setting and, with the input of local collaborators, adapted for cross-cultural data collection. Minimal language demands and the web-app implementation allow fast and easy contextual adaptations to each community. The TANGO--CC captures individual- and community-level variation and shows good internal consistency in a data set from 2.5- to 11-year-old children from 17 diverse communities. Within-community variation outweighed between-community variation. We provide an open-source website for researchers to customize and use the task. The TANGO--CC can be used to assess basic social cognition in diverse communities and provides a roadmap for researching community-level and individual-level differences across cultures.
}

@@

For decades, researchers have advocated for more diverse samples in psychological research and cautioned against relying solely on convenience samples from the Global North (Arnett, 2008; Henrich et al., 2010; Lillard, 1998).
Despite numerous calls for change, the samples reported in major psychology journals still lack diversity (Apicella et al., 2020; Gutchess \& Rajaram, 2023; Thalmayer et al., 2021).
This hinders progress in theory building and testing: we cannot draw inferences about universal and variable aspects of the human cognitive system from data collected exclusively in one single communities (Krys et al., 2024).
While this sampling bias is often discussed within adult psychology, it is equally relevant for developmental psychology (Nielsen et al., 2017).
Early experiences shape the way children think about and interact with the world and an ontogenetic perspective is needed to explore the foundational aspects of human behavioral diversity (Amir \& McAuliffe, 2020; Broesch et al., 2023; Liebal \& Haun, 2018; Torréns et al., 2023).

There are numerous challenges with collecting cross-cultural, developmental data (Amir \& McAuliffe, 2020; Broesch et al., 2023).
Cross-cultural studies need reliable and valid measures to systematically capture variation between communities and/or individuals.
However, studies on social cognition with US-American and European samples rarely report psychometric information (for a review, see Beaudoin et al., 2020), and the picture further deteriorates when we look at cross-cultural social cognition tasks (Bourdage et al., 2023; Hajdúk et al., 2020; Waschl \& Chen, 2022).
Thus, it is already challenging to find reliable and valid tasks that have measurement sensitivity to detect individual differences within one community, let alone tasks that do so across different communities.
In this paper, we describe the construction and psychometric evaluation of a cross-cultural measure of basic social cognition (gaze following) in children as a concrete example for how to address this problem.

Adapting tasks to diverse communities and assessing their validity and reliability might be especially important in the social-cognitive domain.
Social cognition refers to how an individual processes information in social situations which allows them to understand and predict others' behavior (Adolphs, 1999; Decety, 2020; Frith \& Frith, 2007; Zeigler-Hill et al., 2015).
If, in theory, stimuli used in social cognition tasks should relate to people's everyday experiences, then tasks themselves should be tuned to the features of specific communities.
Indeed, task performance can be diminished when stimuli do not reflect characteristics of the participants' communities (Peña, 2007).
For example, Elfenbein and Ambady (2002) found better emotion recognition for members of the same national, ethnic, or regional group.
Selcuk et al. (2023) concluded that children often attribute mental states more accurately and more frequently to individuals from the same community.

There exists a continuum of approaches that researchers can take to collect cross-cultural data, and the decision for a specific method partly depends on whether researchers aim to increasing the \emph{depth} (culture specificity) or \emph{breadth} (standardization across multiple communities) of our psychological knowledge (Amir \& McAuliffe, 2020).
At one extreme, researchers translate the psychological construct into an individually designed study for each community (termed ``assembly''; He and Vijver (2012), Waschl and Chen (2022)).
While this approach allows greater flexibility and sensitivity to cultural differences, it might not be feasible for studying a multitude of communities as it becomes too demanding and time-consuming.
Due to its specificity, observations are limited to each community and absolute task scores might not be comparable across communities.
A study following this approach is Wefers et al. (2023) who investigated how cultural variations in parenting styles modulated infants' responses to disruptions in social interactions.
While studies in the Global North often apply the Still-Face Paradigm to assess infants' reactions to unresponsive partners, Wefers et al. (2023) reasoned that this paradigm might not capture infants' everyday interaction routines in communities with proximal (\emph{i.e.,} emphasis on body stimulation) parenting styles.
By developing the novel No-Touch Paradigm, they found that indeed infants' responses to unresponsive partners were modulated by the cultural context in which they grew up: Kichwa infants from rural Ecuador showed stronger reactions to unresponsive partners in the No-Touch Paradigm compared to the Still-Face Paradigm, while reactions of urban German infants differed less in both paradigms.

At the other extreme, researchers use the same standardized procedure across diverse communities, potentially providing a simple translation or modification of stimuli to ensure they are culturally appropriate (termed ``adoption'' and ``adaptation'', respectively Waschl \& Chen (2022)).
This approach is less sensitive to each community's unique characteristics but renders quantitative comparisons of data more feasible.
An example following this approach is the Multilingual Assessment Instrument for Narratives {[}MAIN; Gagarina et al. (2012){]}, which assesses narrative abilities in mono- and multilingual children.
Extensive piloting and adaptation of MAIN materials ensured that the instrument is culturally appropriate, robust and suitable for cross-linguistic comparisons (Gagarina et al., 2012), and new and revised language versions are continuously added to the MAIN database (Gagarina \& Lindgren, 2020).

The present paper aims to describe the development and psychometric properties of a standardized social cognition task that can be adapted to diverse communities.
Our task focuses on one of the most fundamental social-cognitive abilities: gaze following, that is, the ability to identify the attentional focus of another agent.
Gaze following develops early in infancy (Del Bianco et al., 2019; Tang et al., 2024) and contributes to social learning, communication, and collaboration (Bohn \& Köymen, 2018; Hernik \& Broesch, 2019; Shepherd, 2010; Tomasello et al., 2007).
While the question how social-environmental and cultural factors impact gaze following was recently posed as one of the big open questions in gaze following research (Astor \& Gredebäck, 2022), studies focusing on cultural variations of gaze following are rare.
Callaghan et al. (2011) investigated gaze following behind barriers in 12- and 17-month-olds from rural Canada (n = 35), Peru (n = 38) and India (n = 65). In their setup, an agent sat next to a wall or container and looked at a toy behind this barrier (experimental condition) or a sticker in front of it (control condition). The researchers then assessed whether and in which conditions the children crawled towards/around the barriers to follow the agent's gaze. While the absolute crawling rates differed across communities, children in all three communities crawled more often to gain visual access when the agent looked at an object behind the barrier compared to in front of it.
Hernik and Broesch (2019) studied 22 infants between 5 to 7 months of age from Vanuatu and used an eye-tracking procedure displaying a local actor looking at one of two objects.
Even though face-to-face interactions are less common in interactions between caregivers and children in Vanuatu than in Western communities, the result patterns of gaze following in Ni-Vanuatu infants resembled those of their Western counterparts: infants from Vanuatu followed the agent's gaze to the target object only when preceded by infant-directed, and not adult-directed, speech.
While these two studies point towards a potential cross-cultural stability of gaze following,
the lack of psychometrically evaluated tasks and the small number of communities studied limit the generalizability of these findings.

The task presented here aims to tackle these issues and builds upon a previously established gaze-following task called `TANGO' (Task for Assessing iNdividual differences in Gaze understanding - Open) by Prein et al. (2023).
The TANGO measures how precisely participants locate an agent's attentional focus.
It reliably measured individual differences in a German child sample and an English-speaking remote adult sample (Prein et al., 2023).
As we cannot claim a task's generalizability and reliability based on mono-cultural samples, we need to assess the TANGO's psychometric properties in a larger cross-cultural sample.
This paper showcases the TANGO--CC (TANGO -- Cross-Cultural), a standardized gaze following task that has been adapted to 13 languages and even more communities, and evaluates its psychometric properties by leveraging a large and diverse data set of 2.5- to 11-year-olds from 17 different communities on five continents (Bohn et al., 2024).
We describe the task's development and provide a tutorial for the open-source website (\url{https://ccp-odc.eva.mpg.de/tango-cc/}).

@@

The TANGO-CC was implemented in Leipzig, Germany, and thoroughly assessed in terms of reliability and validity (Prein et al., 2023).
During this process, the cross-cultural adaptation of the task was prepared within a team of cross-cultural psychologists and cognitive scientists.
In this paper, we assess the TANGO--CC's measurement quality (i.e., variability and reliability) across 17 diverse communities by analyzing the data set from Bohn et al. (2024).
In the following, we describe the different steps in detail.

The TANGO--CC is a screen-based task that measures the imprecision with which participants locate a balloon by following an agent's gaze (see Figure \ref{fig:fig1}).
Participants click or touch the location on the screen where they believe the balloon to be.
Precision is measured as the distance between the participant's click on the screen and the balloon's real position.

During the task development, we decided to implement the task's main functionality independently of the task's appearance. We programmed a function that calculates the x and y coordinates of where the agent's pupil and iris should move to follow the balloon, given the eyes' and balloon's original positions and measures. As the measures of the eyes and balloon are read out dynamically from the image on screen, stimuli can be easily adapted and exchanged. No coordination values for animation are hard-coded into the task's source code. After having programmed this ``backbone'' functionality of the task (\emph{i.e.}, animate the eyes so that they follow the balloon), we added the task's audio instructions and superficial appearance (e.g., background scene, hedge, more agent faces).

This basic version of the TANGO was psychometrically evaluated in a German child sample and an English-speaking remote adult sample and was found to be highly reliable and valid (Prein et al., 2023).
While children became more precise in locating the attentional focus of the agent with age, individuals differed across all age groups and showed no floor- or ceiling effects.
In the Leipzig sample, performance in the TANGO was weakly related to factors of children's daily social environment and could predict children's receptive vocabulary 6 months later.
In a computational cognitive model, Prein et al. (2024) described gaze following as form of social vector following and empirically found that performance in the TANGO was related to children's non-social vector following and visual perspective-taking abilities.
These connections to related constructs indicate the task's convergent validity in the German child sample.

To adapt the task for cross-cultural data collection, we generated a set of human cartoon faces and background scenes with the feedback from local researchers and research assistants.
The stimulus pool was adjusted and expanded until the researchers and research assistants from each target community judged the selected stimuli to be representative of the local population and typical accommodation (see Figure \ref{fig:fig2}).
Audio instructions were translated from English into the corresponding local language(s).
By back-translating these instructions, we ensured the original meaning did not change.
Sometimes, specific words were slightly modified in the target language (e.g., ``bush'' instead of ``hedge'') to ensure that all participants understood the instructions well.
Based on these adaptations, the TANGO--CC could be applied in 17 communities and 13 different languages (Bohn et al., 2024). In the following, we describe how researchers can use and customize the TANGO--CC in more detail.

@@

{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-procedure}

\caption{\textbf{Screenshots of the trials.} In training 1, an agent looks at a balloon that falls to the ground, and participants have to respond by clicking/touching the balloon. In training 2, the balloon falls behind the hedge while its flight is still visible. Participants respond by clicking the hedge where they think the balloon is. In test trials, the balloon's movement and final position are covered by a hedge, and participants respond by clicking the hedge. In the task, all movements are smoothly animated (no still pictures). Yellow frames indicate the time point when participants respond (only illustrative, not shown during the task).}\label{fig:fig1}
\end{figure}

The task consists of three different trial types: training 1, training 2, and test trials (see Figure \ref{fig:fig1}).
In every trial, participants see an agent (boy or girl) looking out of a house with a balloon (red, blue, green, or yellow) in front of them.
The balloon falls down to the ground. The eyes of the agent follow the movement of the balloon in a way that the balloon center and the pupil center always align.
Depending on the trial type, participants have different visual access to the balloon's position.
In training 1, participants see the full trajectory of the balloon and directly have to click the balloon itself.
In training 2, participants see most of the balloon's movement, but a hedge covers the final location.
In test trials, a hedge grows at the beginning of the trial and participants see neither the movement nor the final position of the balloon.
The first trial of each type contains an audio description of the presented events (see supplements of Bohn et al. (2024)).
Notably, the instructions explicitly state that the agent is looking at the balloon.

The outcome variable is the distance between the participant's click and the balloon's center.
Trials can be completed quickly and efficiently so that children can complete 15 trials within 10 minutes, and few children fail to complete the task.
By using self-explanatory animations, language demands are kept to a minimum.
The task uses simple audio instructions, which makes the task accessible to children from different age groups, and no reading skills are needed.
There is no feedback during the task to prevent learning effects across trials.

@@

The order of the agents, balloon colors (red, yellow, green, blue), and balloon positions are each randomized independently.
For the balloon positions, the entire width of the screen (1920 in ``SVG units'') is divided into ten bins.
Exact coordinates (value between 0 far left and 1920 far right) within each bin are then randomly generated.
The number of repetitions for each agent, balloon color, and balloon bin is calculated based on the total number of trials and the number of unique agents, balloon colors, and bins, respectively.
All agents, balloon colors, and bins appear equally often and are not repeated in more than two consecutive trials.
If the total number of trials is not divisible by the number of unique elements, some elements (\emph{i.e.,} some agents, balloon colors, bins) are randomly repeated to make up for the remainder.

@@

When reseachers visit the TANGO--CC's website
(\url{https://ccp-odc.eva.mpg.de/tango-cc/}), they can select the language for audio instructions which are currently available for 13 different languages and five more dialects (see Table 1). To add a new language, researchers have two options:
(1) for using their own audio instructions in the offline version of the task, researchers can download the task, exchange the audio instructions in the dist folder (in the folder sounds \textgreater{} custom) and select ``Custom'' in the language drop down menu.
For detailed instructions, see the TANGO--CC's manual (\url{https://ccp-odc.eva.mpg.de/tango-cc/manual.html}).
(2) For adding a new language in the online version of the task, researchers can contact the first author of this paper. Please note that this option requires new audio recordings by the interested reseachers, which will then be openly available for all users of the task.
All written instructions in the task are solely for the research assistant to help them guide participants through the task; these instructions are solely available in English.
The task can either be started with the default settings or further customized by adapting the numbers of trials, agents, and background scenes.
The default settings use the version applied in Bohn et al. (2024) based on the selected language.

If researchers choose to customize the task (see Figure \ref{fig:fig2}), they can adjust the number of trials for each trial type, but not their sequence.
Specifically, trial types build on each other and participants need to complete each trial type (without skipping any) to understand the structure of the task.
The minimum number of trials per type is 1; the maximum is 100.
Furthermore, researchers can customize backgrounds by selecting one of four different backgrounds.
Finally, researchers can choose from 50 diverse cartoon-like human faces (50\% female, 50\% male) and freely select how many different faces to include (min 1, max 50).
Once all the settings are selected, the customized task is compiled.
To save the selected settings, researchers can bookmark the URL to easily access the customized task.

In the last step, researchers can enter an alphanumeric participant identifier (1 - 8 characters) and enable a webcam recording of the participant, if needed. A webcam recording might prove especially helpful for unsupervised online data collection to ensure that the participant is alone during the task and no help is provided.
The participant identifier and webcam choice has to be provided every time the task is run.

The source code of the task is openly available on GitHub (\url{https://github.com/ccp-eva/tango-cc}).
By directly editing the \texttt{HTML} and \texttt{JavaScript} code, researchers can further modify the task as needed.

We created a public OSF page (\url{https://doi.org/10.17605/OSF.IO/P2EGU}) where we plan to collect data sets that used the TANGO-CC.
Researchers who have collected data using the TANGO--CC can share their data with the community by contacting the first author of this paper or visiting this OSF repository.

@@

\caption{\label{tab:langtab}Current language options available for the audio instructions in the TANGO--CC}

\begin{tabular}{lll}
\toprule
Languages & \multicolumn{1}{c}{Language family} & \multicolumn{1}{c}{Speaker's country of origin}\\
\midrule
Bemba & Bantu & Zambia\\
Chinese & Sino-Tibetan & China\\
English & Indo-European & USA / UK / India / Nigeria / New Zealand\\
German & Indo-European & Germany\\
(≠Akhoe) Hai||om & Khoe-Kwadi & Namibia\\
Khwedam & Khoe-Kwadi & Namibia\\
Lingala & Bantu & Rep. Congo\\
Marathi & Indo-European & India\\
Shona & Bantu & Zimbabwe\\
Spanish & Indo-European & Argentina (Rioplatense Spanish) / Mexico (Mexiquense Spanish)\\
Kiswahili & Bantu & Uganda\\
Turkish & Turkic & Türkiye\\
Yaka & Bantu & Rep. Congo\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} In those cases where more than one speaker's country of origin is listed, the audio instructions were recorded multiple times by different speakers. For example, the English instructions are available in five different versions.}
\end{tablenotes}

@@

{\centering \includegraphics[width=1\linewidth]{../figures/tango-cc-screenshot}

@@

\caption{\textbf{Customizable components of the TANGO--CC.} Researchers can select the language of the audio instructions (see Table 1), the number of trials per trial type, the background, and the agent's face.}\label{fig:fig2}
\end{figure}

@@

The task was implemented in \texttt{JavaScript}, \texttt{HTML}, and \texttt{CSS} and is presented as a web app.
It can be accessed on any modern web browser on any device (e.g., computer or tablet) and does not require prior installation (please note that configurations of browsers and JavaScript may change in the future).
Participant's responses can be recorded on a touchscreen or with a mouse or track pad.
The online version of the task can be used for unsupervised data collection (for example, using online platforms like \emph{Prolific}; see Prein et al. (2023)). The task can be shared easily internationally by providing the URL.
Importantly, the web app implementation does not require a working WIFI connection: An offline version of the task can be downloaded and quickly set up for devices that support Node.js (\url{https://nodejs.org/en}).
This is an especially useful feature for researchers working in locations with limited internet access.

The stimuli are embedded as Scalable Vector Graphics (SVG; an image format that stores image elements via mathematical formulas based on points and lines on a grid).
SVGs ensure that the picture quality, aspect ratio, and relative object positioning are constant. Furthermore, stimuli are added as individual components to the image scene which allows for an easy adaptation of task's elements (in contrast to other image formats that consist of only one combined layer that would need entire replacement).
The task is programmed so that responses are only registered when the participant clicks the relevant part of the screen (i.e., in test trials, when they click the hedge).
Furthermore, clicks are only registered after the voice recordings stop playing.
An audio reminder is played again if no click is registered within 5 seconds.
